SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-12-07 toplas26/examples.tex
yet another update

\section{Extended Examples}
\label{section-examples}

@@

\paragraph{Implementation and Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with the Satisfiability Modulo Fields theory.  To evaluate
performance, we have written and verified gate libraries and small
circuits using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers. Results are presented in Figure \ref{fig-preludetest}. In
summary, verification is efficient, largely due to the performance of
underlying cvc5 verification, with categorically better performance
than can be achieved using previous brute-force methods developed in
$\fieldp{2}$ \cite{skalka-near-ppdp24}.

>>>>

\section{Implementation and Extended Examples}
\label{section-examples}

@@

\subsection{Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with proof engines.  To evaluate
performance, we have written and verified gate libraries
using the GMW protocol for binary circuits as excerpted in
Figure \ref{fig-gmwprepost} in Section \ref{section-metalang}, and for
passive and malicious secure arithmetic circuits using Beaver Triple
multiplication as presented in Figures \ref{fig-beaver} and
\ref{fig-beaver-bdoz} in this Section.  We have considered field sizes
typically used to encode binary, 16 bit, 32 bit, and 64 bit
integers.

In addition to libraries, we have verified 2, 8, and 64-bit vector
zero-test GMW circuits containing 3, 15, and 127 gates respectively,
based on ``Bristol Fashion'' circuits \cite{bristol}. By verified, we
mean automated verification of the zero-test specification expressed
as a \ttt{postcondition}. We considered both the cvc5 Bit-Vector and
Satisfiability Modulo Finite Fields (SMFF) theories as proof engines
for these binary circuits.

Results are presented in Figure \ref{fig-preludetest}. We found that
verification of library components was efficient even up to large
field sizes. Verification of the zero-test circuits revealed a clear
performance advantage for the Bit-Vector theory, which verified
the 64-bit zero test in GMW in less than 7 seconds. In contrast,
it took several minutes to verify even the small 2-bit zero-test
circuit in SMFF, and larger circuits took too long to consider
for a practical evaluation. In all cases, the SMT-based approach
supported categorically better performance
than can be achieved using previous brute-force methods developed for
$\fieldp{2}$ and binary circuits \cite{skalka-near-ppdp24}.
